Turbo fast no compromise gravitational wave parameter estimation

### 2023-01-12 src/tex/ms.tex
Add MCMC references

Given eq. \ref{eq: loglikelihood} and the prior, one can evaluate the posterior
density function over the entire parameter space of interest to obtain the most
probable set of points that are consistent with the data. However, direct
sampling quickly becomes intractable as the dimensionality of the parameter
space increases beyond a few dimensions. Markov chain Monte Carlo (MCMC) is a
common method employed to generate samples when direct sampling is not possible.

In MCMC, the posterior distribution is approximated by a Markov chain that
converges to the target distribution. The Markov chain is constructed by
iteratively proposing a new point in the parameter space based on the current
location of the chain. The proposed point is accepted with a probability that is
usually set to be proportional to the ratio of the posterior density evaluated
at the proposed point and the current point. The chain can either accept the
proposal and move to the new location or reject the proposal and stay at the
current location. This process is repeated until the chain converges to the
target distribution. The samples generated by the chain are then used to
estimate the quantities of interest, such as the mean and credible intervals of
the source parameters. In practice, since we do not know the target distribution
ahead of time, the MCMC process is usually repeated until a certain criterion is
met, such as a Gelman-Rubin convergence statistic \cite{10.2307/2246093} lower than
a threshold or simply after a certain number of iterations.

@@

However, as we are dealing with higher dimensional problems, even the optimally
tuned Gaussian transition kernel does not guarantee good performance. In order
to have a reasonable acceptance rate, the variance of the Gaussian has to be
smaller in a higher dimensional space, which means the transition kernel is in
general making smaller and smaller steps as we increase the dimensionality.

>>>>

Given eq. \ref{eq: loglikelihood} and the prior, one can evaluate the posterior
density function over the entire parameter space of interest to obtain the most
probable set of points that are consistent with the data. However, direct
sampling quickly becomes intractable as the dimensionality of the parameter
space increases beyond a few dimensions. Markov chain Monte Carlo (MCMC)
\cite{gelmanbda04} is a common method employed to generate samples when direct
sampling is not possible.

In MCMC, the posterior distribution is approximated by a Markov chain that
converges to the target distribution \cite{10.1214/aos/1176325750}. The Markov
chain is constructed by iteratively proposing a new point in the parameter space
based on the current location of the chain. The proposed point is accepted with
a probability that is usually set to be proportional to the ratio of the
posterior density evaluated at the proposed point and the current point. The
chain can either accept the proposal and move to the new location or reject the
proposal and stay at the current location. This process is repeated until the
chain converges to the target distribution. The samples generated by the chain
are then used to estimate the quantities of interest, such as the mean and
credible intervals of the source parameters. In practice, since we do not know
the target distribution ahead of time, the MCMC process is usually repeated
until a certain criterion is met, such as a Gelman-Rubin convergence statistic
\cite{10.2307/2246093} lower than a threshold or simply after a certain number
of iterations.

@@

However, as we are dealing with higher dimensional problems, even the optimally
tuned Gaussian transition kernel does not guarantee good performance. In order
to have a reasonable acceptance rate, the variance of the Gaussian has to be
smaller in a higher dimensional space, which means the transition kernel is in
general making smaller and smaller steps as we increase the dimensionality
\cite{2017arXiv170102434B}.
